\huge{ \emph{Supplement to} Algorithms For Shaping a Particle Swarm\\ With a Shared Control Input Using Boundary Interaction}

### 2016-09-07 RA-L/appendix.tex
Worked on intro
compressed some images, made appendix able to be added easily.

\documentclass[conference]{IEEEtran}
\usepackage{times}

% numbers option provides compact numerical references in the text. 
\usepackage[numbers]{natbib}
\usepackage{multicol}
\usepackage[bookmarks=true]{hyperref}

\usepackage{bbm}
\usepackage{calc}
\usepackage{url}
\usepackage{hyperref}
\hypersetup{
  colorlinks =true,
  urlcolor = black,
  linkcolor = black
}
\usepackage{graphicx}
\usepackage[cmex10]{amsmath}
\usepackage{bm}
\usepackage{amssymb}
\usepackage{rotating}

%\usepackage{xfrac}
\usepackage{nicefrac}
\usepackage{cite}
\usepackage[caption=false,font=footnotesize]{subfig}
\usepackage[usenames, dvipsnames]{color}
\usepackage{colortbl}
%\usepackage{caption}

%\usepackage{wrapfig}
\usepackage{overpic}
%\usepackage{subfigure}
%\usepackage{textcomp}
\graphicspath{{./pictures/pdf/},{./pictures/ps/},{./pictures/png/},{./pictures/jpg/}}
\usepackage{breqn} %for breaking equations automatically
\usepackage[ruled]{algorithm}
\usepackage{algpseudocode}
%\usepackage{algorithmic}
\usepackage{multirow}
\usepackage{todonotes}

%\newcommand{\todo}[1]{\vspace{5 mm}\par \noindent \framebox{\begin{minipage}[c]{0.98 \columnwidth} \ttfamily\flushleft \textcolor{red}{#1}\end{minipage}}\vspace{5 mm}\par}
% uncomment this to hide all red todos
%\renewcommand{\todo}{}

%% ABBREVIATIONS
\newcommand{\qstart}{q_{\text{start}}}
\newcommand{\qgoal}{q_{\text{goal}}}
\newcommand{\pstart}{p_{\text{start}}}
\newcommand{\pgoal}{p_{\text{goal}}}
\newcommand{\xstart}{x_{\text{start}}}
\newcommand{\xgoal}{x_{\text{goal}}}
\newcommand{\ystart}{y_{\text{start}}}
\newcommand{\ygoal}{y_{\text{goal}}}
\newcommand{\gammastart}{\gamma_{\text{start}}}
\newcommand{\gammagoal}{\gamma_{\text{goal}}}
\providecommand{\proc}[1]{\textsc{#1}}

\newcommand{\ARLfull}{Aero\-space Ro\-bot\-ics La\-bora\-tory }
\newcommand{\ARL}{\textsc{arl}}
\newcommand{\JPL}{\textsc{jpl}}
\newcommand{\PRM}{\textsc{prm}}

\newcommand{\CM}{\textsc{cm}}
\newcommand{\SVM}{\textsc{svm}}
\newcommand{\NN}{\textsc{nn}}
\newcommand{\prm}{\textsc{prm}}
\newcommand{\lemur}{\textsc{lemur}}
\newcommand{\Lemur}{\textsc{Lemur}}
\newcommand{\LP}{\textsc{lp}} 
\newcommand{\SOCP}{\textsc{socp}}
\newcommand{\SDP}{\textsc{sdp}}
\newcommand{\NP}{\textsc{np}}
\newcommand{\SAT}{\textsc{sat}}
\newcommand{\LMI}{\textsc{lmi}}
\newcommand{\hrp}{\textsc{hrp\nobreakdash-2}}
\newcommand{\DOF}{\textsc{dof}}
\newcommand{\UIUC}{\textsc{uiuc}}
%% MACROS

\providecommand{\abs}[1]{\left\lvert#1\right\rvert}
\providecommand{\norm}[1]{\left\lVert#1\right\rVert}
\providecommand{\normn}[2]{\left\lVert#1\right\rVert_#2}
\providecommand{\dualnorm}[1]{\norm{#1}_\ast}
\providecommand{\dualnormn}[2]{\norm{#1}_{#2\ast}}
\providecommand{\set}[1]{\lbrace\,#1\,\rbrace}
\providecommand{\cset}[2]{\lbrace\,{#1}\nobreak\mid\nobreak{#2}\,\rbrace}
\providecommand{\lscal}{<}
\providecommand{\gscal}{>}
\providecommand{\lvect}{\prec}
\providecommand{\gvect}{\succ}
\providecommand{\leqscal}{\leq}
\providecommand{\geqscal}{\geq}
\providecommand{\leqvect}{\preceq}
\providecommand{\geqvect}{\succeq}
\providecommand{\onevect}{\mathbf{1}}
\providecommand{\zerovect}{\mathbf{0}}
\providecommand{\field}[1]{\mathbb{#1}}
\providecommand{\C}{\field{C}}
\providecommand{\R}{\field{R}}
\newcommand{\Cspace}{\mathcal{Q}}
\newcommand{\Uspace}{\mathcal{U}}
\providecommand{\Fspace}{\Cspace_\text{free}}
\providecommand{\Hcal}{$\mathcal{H}$}
\providecommand{\Vcal}{$\mathcal{V}$}
\DeclareMathOperator{\conv}{conv}
\DeclareMathOperator{\cone}{cone}
\DeclareMathOperator{\homog}{homog}
\DeclareMathOperator{\domain}{dom}
\DeclareMathOperator{\range}{range}
\DeclareMathOperator{\sign}{sgn}
\providecommand{\polar}{\triangle}
\providecommand{\ainner}{\underline{a}}
\providecommand{\aouter}{\overline{a}}
\providecommand{\binner}{\underline{b}}
\providecommand{\bouter}{\overline{b}}
\newcommand{\D}{\nobreakdash-\textsc{d}}
%\newcommand{\Fspace}{\mathcal{F}}
\providecommand{\Fspace}{\Cspace_\text{free}}
\providecommand{\free}{\text{\{}\mathsf{free}\text{\}}}
\providecommand{\iff}{\Leftrightarrow}
\providecommand{\subinner}[1]{#1_{\text{inner}}}
\providecommand{\subouter}[1]{#1_{\text{outer}}}
\providecommand{\Ppoly}{\mathcal{X}}
\providecommand{\Pproj}{\mathcal{Y}}
\providecommand{\Pinner}{\subinner{\Pproj}}
\providecommand{\Pouter}{\subouter{\Pproj}}
\DeclareMathOperator{\argmax}{arg\,max}
\providecommand{\Aineq}{B}
\providecommand{\Aeq}{A}
\providecommand{\bineq}{u}
\providecommand{\beq}{t}
\DeclareMathOperator{\area}{area}
\newcommand{\contact}[1]{\Cspace_{#1}}
\newcommand{\feasible}[1]{\Fspace_{#1}}
\newcommand{\dd}{\; \mathrm{d}}
\newcommand{\figwid}{0.22\columnwidth}
\newcommand{\TRUE}{\textbf{true}}
\newcommand{\FALSE}{\textbf{false}}
\DeclareMathOperator{\atan2}{atan2}

\newtheorem{theorem}{Theorem}
\newtheorem{definition}[theorem]{Definition}
\newtheorem{lemma}[theorem]{Lemma}

\pdfinfo{
   /Author (Shiva Shahrokhi, Arun Mahadev, and Aaron T. Becker)
   /Title  (Supplement toAlgorithms For Shaping a Particle Swarm With a Shared Control Input Using Boundary Interaction)
   /CreationDate (D:20160129120000)
   /Subject (Simple Robots)
   /Keywords (Robots;Uniform Control Inputs)
}

\begin{document}

@@

\maketitle

\begin{abstract}
%Also 
Includes algorithms and equations too lengthy for main paper, but potentially useful for the community.
Also links to videos and demonstration code for the algorithms.
\end{abstract}

@@

\subsection{TwoRobotPosition.mp4}
Animates Algs. 1, 2, 3 in Mathematica to show how two robots can be arbitrarily positioned in a square workspace. In this video the desired initial and ending positions of the two robots are manipulated, and the path that the robots should follow is drawn. The video ends with an extreme case where the robots must exchange positions. 
Full resolution video: \url{https://youtu.be/5TWlw7vThsM}.
An online demonstration and source code of the algorithm are at \citet{Shahrokhi2015mathematicaParticle}.

\subsection{Arranging a robot swarm with global inputs and wall friction [discrete] }
An implementation of Alg. 4  in {\sc Matlab} that illustrates how the two robots positioning algorithm is extendable to $n$ robots. In this video all  robots gets the same input, but by exploiting wall friction each robot reaches its goal, the formation "UH".
Full resolution video: \url{https://youtu.be/uhpsAyPwKeI}.
Full code is available at \citet{Arun2015}.

@@

%%%%%%%%%%%%%%%
%% Use plainnat to work nicely with natbib. 
\bibliographystyle{plainnat}
\bibliography{IEEEabrv,ShapingSwarmFrictionSharedInput}
\end{document}

>>>>

%
%\documentclass[conference]{IEEEtran}
%\usepackage{times}
%
%% numbers option provides compact numerical references in the text. 
%\usepackage[numbers]{natbib}
%\usepackage{multicol}
%\usepackage[bookmarks=true]{hyperref}
%
%\usepackage{bbm}
%\usepackage{calc}
%\usepackage{url}
%\usepackage{hyperref}
%\hypersetup{
%  colorlinks =true,
%  urlcolor = black,
%  linkcolor = black
%}
%\usepackage{graphicx}
%\usepackage[cmex10]{amsmath}
%\usepackage{bm}
%\usepackage{amssymb}
%\usepackage{rotating}
%
%
%%\usepackage{xfrac}
%\usepackage{nicefrac}
%\usepackage{cite}
%\usepackage[caption=false,font=footnotesize]{subfig}
%\usepackage[usenames, dvipsnames]{color}
%\usepackage{colortbl}
%%\usepackage{caption}
%
%%\usepackage{wrapfig}
%\usepackage{overpic}
%%\usepackage{subfigure}
%%\usepackage{textcomp}
%\graphicspath{{./pictures/pdf/},{./pictures/ps/},{./pictures/png/},{./pictures/jpg/}}
%\usepackage{breqn} %for breaking equations automatically
%\usepackage[ruled]{algorithm}
%\usepackage{algpseudocode}
%%\usepackage{algorithmic}
%\usepackage{multirow}
%\usepackage{todonotes}
%
%%\newcommand{\todo}[1]{\vspace{5 mm}\par \noindent \framebox{\begin{minipage}[c]{0.98 \columnwidth} \ttfamily\flushleft \textcolor{red}{#1}\end{minipage}}\vspace{5 mm}\par}
%% uncomment this to hide all red todos
%%\renewcommand{\todo}{}
%
%%% ABBREVIATIONS
%\newcommand{\qstart}{q_{\text{start}}}
%\newcommand{\qgoal}{q_{\text{goal}}}
%\newcommand{\pstart}{p_{\text{start}}}
%\newcommand{\pgoal}{p_{\text{goal}}}
%\newcommand{\xstart}{x_{\text{start}}}
%\newcommand{\xgoal}{x_{\text{goal}}}
%\newcommand{\ystart}{y_{\text{start}}}
%\newcommand{\ygoal}{y_{\text{goal}}}
%\newcommand{\gammastart}{\gamma_{\text{start}}}
%\newcommand{\gammagoal}{\gamma_{\text{goal}}}
%\providecommand{\proc}[1]{\textsc{#1}}
%
%
%\newcommand{\ARLfull}{Aero\-space Ro\-bot\-ics La\-bora\-tory }
%\newcommand{\ARL}{\textsc{arl}}
%\newcommand{\JPL}{\textsc{jpl}}
%\newcommand{\PRM}{\textsc{prm}}
%
%\newcommand{\CM}{\textsc{cm}}
%\newcommand{\SVM}{\textsc{svm}}
%\newcommand{\NN}{\textsc{nn}}
%\newcommand{\prm}{\textsc{prm}}
%\newcommand{\lemur}{\textsc{lemur}}
%\newcommand{\Lemur}{\textsc{Lemur}}
%\newcommand{\LP}{\textsc{lp}} 
%\newcommand{\SOCP}{\textsc{socp}}
%\newcommand{\SDP}{\textsc{sdp}}
%\newcommand{\NP}{\textsc{np}}
%\newcommand{\SAT}{\textsc{sat}}
%\newcommand{\LMI}{\textsc{lmi}}
%\newcommand{\hrp}{\textsc{hrp\nobreakdash-2}}
%\newcommand{\DOF}{\textsc{dof}}
%\newcommand{\UIUC}{\textsc{uiuc}}
%%% MACROS
%
%
%\providecommand{\abs}[1]{\left\lvert#1\right\rvert}
%\providecommand{\norm}[1]{\left\lVert#1\right\rVert}
%\providecommand{\normn}[2]{\left\lVert#1\right\rVert_#2}
%\providecommand{\dualnorm}[1]{\norm{#1}_\ast}
%\providecommand{\dualnormn}[2]{\norm{#1}_{#2\ast}}
%\providecommand{\set}[1]{\lbrace\,#1\,\rbrace}
%\providecommand{\cset}[2]{\lbrace\,{#1}\nobreak\mid\nobreak{#2}\,\rbrace}
%\providecommand{\lscal}{<}
%\providecommand{\gscal}{>}
%\providecommand{\lvect}{\prec}
%\providecommand{\gvect}{\succ}
%\providecommand{\leqscal}{\leq}
%\providecommand{\geqscal}{\geq}
%\providecommand{\leqvect}{\preceq}
%\providecommand{\geqvect}{\succeq}
%\providecommand{\onevect}{\mathbf{1}}
%\providecommand{\zerovect}{\mathbf{0}}
%\providecommand{\field}[1]{\mathbb{#1}}
%\providecommand{\C}{\field{C}}
%\providecommand{\R}{\field{R}}
%\newcommand{\Cspace}{\mathcal{Q}}
%\newcommand{\Uspace}{\mathcal{U}}
%\providecommand{\Fspace}{\Cspace_\text{free}}
%\providecommand{\Hcal}{$\mathcal{H}$}
%\providecommand{\Vcal}{$\mathcal{V}$}
%\DeclareMathOperator{\conv}{conv}
%\DeclareMathOperator{\cone}{cone}
%\DeclareMathOperator{\homog}{homog}
%\DeclareMathOperator{\domain}{dom}
%\DeclareMathOperator{\range}{range}
%\DeclareMathOperator{\sign}{sgn}
%\providecommand{\polar}{\triangle}
%\providecommand{\ainner}{\underline{a}}
%\providecommand{\aouter}{\overline{a}}
%\providecommand{\binner}{\underline{b}}
%\providecommand{\bouter}{\overline{b}}
%\newcommand{\D}{\nobreakdash-\textsc{d}}
%%\newcommand{\Fspace}{\mathcal{F}}
%\providecommand{\Fspace}{\Cspace_\text{free}}
%\providecommand{\free}{\text{\{}\mathsf{free}\text{\}}}
%\providecommand{\iff}{\Leftrightarrow}
%\providecommand{\subinner}[1]{#1_{\text{inner}}}
%\providecommand{\subouter}[1]{#1_{\text{outer}}}
%\providecommand{\Ppoly}{\mathcal{X}}
%\providecommand{\Pproj}{\mathcal{Y}}
%\providecommand{\Pinner}{\subinner{\Pproj}}
%\providecommand{\Pouter}{\subouter{\Pproj}}
%\DeclareMathOperator{\argmax}{arg\,max}
%\providecommand{\Aineq}{B}
%\providecommand{\Aeq}{A}
%\providecommand{\bineq}{u}
%\providecommand{\beq}{t}
%\DeclareMathOperator{\area}{area}
%\newcommand{\contact}[1]{\Cspace_{#1}}
%\newcommand{\feasible}[1]{\Fspace_{#1}}
%\newcommand{\dd}{\; \mathrm{d}}
%\newcommand{\figwid}{0.22\columnwidth}
%\newcommand{\TRUE}{\textbf{true}}
%\newcommand{\FALSE}{\textbf{false}}
%\DeclareMathOperator{\atan2}{atan2}
%
%
%\newtheorem{theorem}{Theorem}
%\newtheorem{definition}[theorem]{Definition}
%\newtheorem{lemma}[theorem]{Lemma}
%
%
%\pdfinfo{
%   /Author (Shiva Shahrokhi, Arun Mahadev, and Aaron T. Becker)
%   /Title  (Supplement toAlgorithms For Shaping a Particle Swarm With a Shared Control Input Using Boundary Interaction)
%   /CreationDate (D:20160129120000)
%   /Subject (Simple Robots)
%   /Keywords (Robots;Uniform Control Inputs)
%}
%
%\begin{document}

@@

\newpage
\maketitle

{\huge{ \emph{Supplement to} 
Algorithms For Shaping a Particle Swarm\\ With a Shared Control Input Using Boundary Interaction}}\\

\begin{abstract}
%Also 
Includes algorithms and equations too lengthy for main paper, but potentially useful for the community.
Also links to videos and demonstration code for the algorithms.

\end{abstract}

@@

\subsection{Steering 2 Particles with Shared Controls Using Wall Friction}
Animates Algs. 1, 2, 3 in Mathematica to show how two robots can be arbitrarily positioned in a square workspace. In this video the desired initial and ending positions of the two robots are manipulated, and the path that the robots should follow is drawn. The video ends with an extreme case where the robots must exchange positions. 
Full resolution video: \url{https://youtu.be/5TWlw7vThsM}.
An online demonstration and source code of the algorithm are at \citet{Shahrokhi2015mathematicaParticle}.

\subsection{Arranging a robot swarm with global inputs and wall friction [discrete] }
An implementation of Alg. 4  in {\sc Matlab} that illustrates how the two robots positioning algorithm is extendable to $n$ robots. In this video all  robots gets the same input, but by exploiting wall friction each robot reaches its goal, the formation "UH".
Full resolution video: \url{https://youtu.be/uhpsAyPwKeI}.
Full code is available at \citet{Arun2015}.
Note that this code uses discretized version of Algorithm 3.  The continuous-movement version is illustrated in Fig.\ref{fig:PositionNrobotsCont}.
\begin{figure}
\begin{center}
	\includegraphics[width=1.0\columnwidth]{PositionNrobotsComp.pdf}
\end{center}
\vspace{-1em}
\caption{\label{fig:PositionNrobotsCont}
Illustration of Alg.\ \ref{alg:PosControlNRobots}, $n$ robot position control  using wall friction.
}
\end{figure}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section*{Acknowledgments}
This work was supported by the National Science Foundation under Grant No.\ \href{http://nsf.gov/awardsearch/showAward?AWD_ID=1553063}{ [IIS-1553063]}.

%%%%%%%%%%%%%%%
%% Use plainnat to work nicely with natbib. 
\bibliographystyle{plainnat}
\footnotesize
\bibliography{IEEEabrv,ShapingSwarmFrictionSharedInput}
%\end{document}
